### 2015-12-08 mirror-descent.tex
Many improvements
1) Add conclusion
2) Add limits and their explanations
3) Add many bibliographic references
4) Fix formatting for most .tex files

\textsc{Mirror Descent} is a generic algorithm similar to \textsc{Follow The
Regularized Leader} but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, Bregman
divergence, $\Breg_{R_t}(u,v) = R(u) - R(v) - \langle \grad R(v), u - v
\rangle$ needs to be defined. This is done by choosing a subgradient map $\grad
R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient of
$R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{Mirror Descent}.  Proof
can be found in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.
For completeness we give a proof in~\ref{section:mirror-descent-proofs}.

@@

Several existing algorithms are special cases of \textsc{Mirror Descent}. Most
prominent example is projected gradient descent defined by $w_{t+1} = \Pi_K(w_t
- \eta_t \ell_t)$ where $\Pi_K$ is the Euclidean projection to $K$ and
$\eta_t>0$ is the step size.  Projected gradient descent is an instance of
\textsc{Mirror Descent} with regularizer $R_t(w) = \frac{1}{2\eta_t}\|w\|_2^2$.
A special case of projected gradient descent with step size $\eta_t =
\frac{1}{\sqrt{t}}$ is Zinkevich's \textsc{Generalized Infinitesimal Gradient
Ascent} (GIGA) algorithm~\cite{Zinkevich-2003}. Full-matrix and diagonal
versions of \textsc{AdaGrad with Composite Mirror Descent
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{Mirror
Descent} for any bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. When $d=1$, both algorithms are equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free generalization of
Zinkevich's GIGA algorithm. In particular, when $\|\ell_i\|_2 = 1$ for all $i$,
\textsc{Mirror Descent} with regularizer \eqref{equation:ada-grad-regularizer}
coincides with GIGA.

\textsc{Exponentially-Weighted Average Forecaster}~\cite[Chapter
2]{Cesa-Bianchi-Lugosi-2006} with constant learning rate $\eta$ for the problem
of prediction with expert advice is an instance of \textsc{Mirror Descent} for
the probability simplex $K = \{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1
\}$ with negative entropy regularizer $R_t(w) = \frac{1}{\eta} \sum_{j=1}^d w_j
\ln w_j$ where $R_t:K \to \R$. Note that this algorithm is \emph{not}
scale-free.

Replacing $\frac{1}{2}\|w\|_2^2$ in equation \eqref{equation:ada-grad-regularizer} with
an arbitrary convex function $R:K \to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free Mirror Descent} with
regularizer $R$.  Generalizing existing regret bound for
\textsc{AdaGrad}~\cite{Duchi-Hazan-Singer-2011} we can upper bound its regret.
Proof is a generalization of the proof
of~\cite{Duchi-Shalev-Shwartz-Singer-Tewari-2010,Duchi-Hazan-Singer-2011} and
it can be found can be found in~\ref{section:mirror-descent-proofs}.

@@

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$ there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free Mirror Descent} with
regularizer $R(w) = \frac{1}{2}\|w\|_2^2$, Zinkevich's \textsc{GIGA} algorithm,
and both versions of \textsc{AdaGrad with Composite Mirror Descent Update}
satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}

The second counter-example is stated as Theorem~\ref{theorem:second-counter-example}
below.  The decision set is the $d$-dimensional probability simplex $K = \{ w
\in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$ and the regularizer is the
negative entropy $R(w) = \sum_{j=1}^d w_j \ln w_j$.  Negative entropy is
$1$-strongly convex with respect to $\|\cdot\|_1$ and the dual norm of
$\|\cdot\|_1$ is \mbox{$\|\cdot\|_\infty$}.  The corresponding Bregman
divergence is the Kullback-Leibler divergence $\Breg_R(u,v) = \sum_{j=1}^d u_j
\ln(u_j/v_j)$.  Note that despite that negative entropy is upper- and
lower-bounded, Kullback-Leibler divergence is unbounded from above.

\begin{theorem}[Second Counter-Example]
\label{theorem:second-counter-example}
Let $d \ge 2$, let $V = \R^d$, and let $K = \{ w \in V ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$
be the $d$-dimensional probability simplex.  For any $T \ge 120$
there exists a sequence of loss vectors $\ell_1, \ell_2, \dots, \ell_T \in V^*$
such that $\|\ell_1\|_\infty = \|\ell_2\|_\infty = \dots = \|\ell_T\|_\infty =
1$ and \textsc{Scale-Free Mirror Descent} with regularizer $R(w) = \sum_{j=1}^d
w_j \ln w_j$ satisfies
$$
\Regret_T \ge \frac{T}{6} \; .
$$
\end{theorem}

>>>>

\textsc{Mirror Descent}\footnote{The algorithm was originally proposed in
\cite{Nemirovski-Yudin-1983} and later analyzed in~\cite{Beck-Teboulle-2003}.}
is a generic algorithm similar to \textsc{Follow The Regularized Leader} but
quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, Bregman
divergence, $\Breg_{R_t}(u,v) = R(u) - R(v) - \langle \grad R(v), u - v
\rangle$ needs to be defined. This is done by choosing a subgradient map $\grad
R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient of
$R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{Mirror Descent}.  Proof
can be found
in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.  For
completeness we give a proof in~\ref{section:mirror-descent-proofs}.

@@

Several existing algorithms are special cases of \textsc{Mirror Descent}. Most
prominent example is \textsc{Projected Gradient Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K(w_t - \eta_t \ell_t)
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{Mirror Descent} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of projected gradient descent with
step size $\eta_t = \frac{1}{\sqrt{t}}$ is Zinkevich's \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA) algorithm~\cite{Zinkevich-2003}.
Full-matrix and diagonal versions of \textsc{AdaGrad with Composite Mirror
Descent Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of
\textsc{Mirror Descent} for any bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. When $d=1$, both algorithms are equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of Zinkevich's GIGA algorithm. In particular, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{Mirror Descent} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

\textsc{Exponentially-Weighted Average
Forecaster}~\cite[Chapter~2]{Cesa-Bianchi-Lugosi-2006} with constant learning
rate $\eta$ for the problem of prediction with expert advice is an instance of
\textsc{Mirror Descent} for the probability simplex $K = \{ w \in \R^d ~:~ w_j
\ge 0, \sum_{j=1}^d w_j = 1 \}$ with negative entropy regularizer $R_t(w) =
\frac{1}{\eta} \sum_{j=1}^d w_j \ln w_j$ where $R_t:K \to \R$. Note that this
algorithm is \emph{not} scale-free.

Replacing $\frac{1}{2}\|w\|_2^2$ in equation
\eqref{equation:ada-grad-regularizer} with an arbitrary convex function $R:K
\to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free Mirror Descent} with
regularizer $R$. Similar to \textsc{SOLO FTRL}, the regularizer
\eqref{equation:scale-free-mirror-descent} does not uniquely define
the \textsc{Mirror Descent}
minimizer
$w_{t+1} = \argmin_{w \in K} \left(\langle \ell_t, w \rangle + \Breg_{R_t}(w,
w_t) \right)$ when $\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}$ is zero.
This happens when the loss vectors $\ell_1, \ell_2, \dots, \ell_t$ are all
zero (and in particular for $t=0$). In this case, we define
$w_{t+1} = \argmin_{w \in K} R(w)$ which agrees with
$w_{t+1} = \lim_{a \to 0^+} \argmin_{w \in K} a \Breg_{R}(w, w_t)$.

Generalizing existing regret bound for
\textsc{AdaGrad}~\cite{Duchi-Hazan-Singer-2011} (see
also~\cite{Duchi-Shalev-Shwartz-Singer-Tewari-2010,Rakhlin-Sridharan-2013}) we
can upper bound regret of \textsc{Scale-Free Mirror Descent}.  Proof is
in~\ref{section:mirror-descent-proofs}.

@@

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$, there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free Mirror Descent} with
regularizer $R(w) = \frac{1}{2}\|w\|_2^2$, Zinkevich's \textsc{GIGA} algorithm,
and both versions of \textsc{AdaGrad with Composite Mirror Descent Update}
satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}

The second counter-example is stated as
Theorem~\ref{theorem:second-counter-example} below.  The decision set is the
$d$-dimensional probability simplex $K = \{ w \in \R^d ~:~ w_j \ge 0,
\sum_{j=1}^d w_j = 1 \}$ and the regularizer is the negative entropy $R(w) =
\sum_{j=1}^d w_j \ln w_j$.  Negative entropy is $1$-strongly convex with
respect to $\|\cdot\|_1$ and the dual norm of $\|\cdot\|_1$ is
\mbox{$\|\cdot\|_\infty$}.  The corresponding Bregman divergence is the
Kullback-Leibler divergence $\Breg_R(u,v) = \sum_{j=1}^d u_j \ln(u_j/v_j)$.
Note that despite that negative entropy is upper- and lower-bounded,
Kullback-Leibler divergence can be arbitrarily large.

\begin{theorem}[Second Counter-Example]
\label{theorem:second-counter-example}
Let $d \ge 2$, let $V = \R^d$, and let $K = \{ w \in V ~:~ w_j \ge 0,
\sum_{j=1}^d w_j = 1 \}$ be the $d$-dimensional probability simplex.  For any
$T \ge 120$, there exists a sequence of loss vectors $\ell_1, \ell_2, \dots,
\ell_T \in V^*$ such that $\|\ell_1\|_\infty = \|\ell_2\|_\infty = \dots =
\|\ell_T\|_\infty = 1$ and \textsc{Scale-Free Mirror Descent} with regularizer
$R(w) = \sum_{j=1}^d w_j \ln w_j$ satisfies
$$
\Regret_T \ge \frac{T}{6} \; .
$$
\end{theorem}

### 2015-12-08 per-coordinate.tex
Many improvements
1) Add conclusion
2) Add limits and their explanations
3) Add many bibliographic references
4) Fix formatting for most .tex files

Abstractly, we assume that the decision set is a Cartesian product $K=K_1
\times K_2 \times \dots \times K_d$ of a finite number of convex sets.  On each
factor $K_j$, $i=1,2,\dots,d$, we can run any OLO algorithm separately and we
denote by $\Regret_T^{(j)}(u_j)$ its regret with respect to $u_j \in K_j$. The
overall regret with respect to any $u=(u_1, u_2, \dots, u_d) \in K$ can be
written as
$$
\Regret_T(u) = \sum_{j=1}^d \Regret_T^{(j)}(u_j) \; .
$$
If the algorithm for each factor is scale-free, the overall algorithm is
clearly scale-free as well.  Using \textsc{AdaFTRL} or \textsc{SOLO FTRL} for
each factor $K_j$, we generalize and improve existing regret bounds
\cite{McMahan-Streeter-2010,Duchi-Hazan-Singer-2011} for algorithms with per-coordinate
learning rates.

>>>>

Abstractly, we assume that the decision set is a Cartesian product $K=K_1
\times K_2 \times \dots \times K_d$ of a finite number of convex sets.  On each
factor $K_j$, $j=1,2,\dots,d$, we can run any OLO algorithm separately and we
denote by $\Regret_T^{(j)}(u_j)$ its regret with respect to $u_j \in K_j$. The
overall regret with respect to any $u=(u_1, u_2, \dots, u_d) \in K$ can be
written as
$$
\Regret_T(u) = \sum_{j=1}^d \Regret_T^{(j)}(u_j) \; .
$$
If the algorithm for each factor is scale-free, the overall algorithm is
clearly scale-free as well.  Using \textsc{AdaFTRL} or \textsc{SOLO FTRL} for
each factor $K_j$, we generalize and improve existing regret bounds
\cite{McMahan-Streeter-2010,Duchi-Hazan-Singer-2011} for algorithms with
per-coordinate learning rates.

### 2015-12-08 preliminaries-proofs.tex
Many improvements
1) Add conclusion
2) Add limits and their explanations
3) Add many bibliographic references
4) Fix formatting for most .tex files

\begin{proof}[Proof of Property 6 of Proposition~\ref{proposition:conjugate-properties}]
To bound $\Breg_{f^*}(x,y)$ we add a non-negative divergence term
$\Breg_{f^*}(y,x)$.
\begin{align*}
\Breg_{f^*}(x, y)
& \le \Breg_{f^*}(x,y) + \Breg_{f^*}(y,x)
= \langle x - y, \grad f^*(x) - \grad f^*(y) \rangle \\
& \le \|x - y\|_* \cdot \| \grad f^*(x) - \grad f^*(y) \|
\le D \|x - y\|_* \; ,
\end{align*}
where we have used H\"older's inequality and Part 7 of the Proposition.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:generic-regret-bound}]
By Fenchel-Young inequality,
\begin{align*}
\sum_{t=1}^T \left( R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) \right)
& = R_{T+1}^*(-L_T) - R_1^*(0) \\
& \ge - \langle L_T, u \rangle - R_{T+1}(u)  - R_1^*(0) \\
& = - R_{T+1}(u)  - R_1^*(0) - \sum_{t=1}^T \langle \ell_t, u \rangle \; .
\end{align*}
We add $\sum_{t=1}^T \langle \ell_t, w_t \rangle$ to both sides and we obtain
$\Regret_T(u)$ on the right side. After rearrangement of the terms, we get an upper bound
on the regret:
\begin{align*}
\Regret_T(u)
& = \sum_{t=1}^T \langle \ell_t, w_t \rangle - \sum_{t=1}^T \langle \ell_t, u \rangle \\
& \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^T \left( R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, w_t \rangle \right) \; .
\end{align*}
By Proposition~\ref{proposition:conjugate-properties}, part 2, we have $w_t =
\grad R_t^*(-L_{t-1})$ and therefore we can rewrite the sum in last expression as
\begin{align*}
& \sum_{t=1}^T R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, w_t \rangle \\
& = \sum_{t=1}^T R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, \grad R_t^*(-L_{t-1}) \rangle \\
& = \sum_{t=1}^T R_t^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, \grad R_t^*(-L_{t-1}) \rangle - R_t^*(-L_t) + R_{t+1}^*(-L_t) \\
& = \sum_{t=1}^T \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
\end{align*}
This finishes the proof.
\end{proof}

>>>>

\begin{proof}[Proof of Property 6 of Proposition~\ref{proposition:conjugate-properties}]
To bound $\Breg_{f^*}(x,y)$ we add a non-negative divergence term
$\Breg_{f^*}(y,x)$.
\begin{align*}
\Breg_{f^*}(x, y)
& \le \Breg_{f^*}(x,y) + \Breg_{f^*}(y,x)
= \langle x - y, \grad f^*(x) - \grad f^*(y) \rangle \\
& \le \|x - y\|_* \cdot \| \grad f^*(x) - \grad f^*(y) \|
\le D \|x - y\|_* \; ,
\end{align*}
where we have used H\"older's inequality and property 7 of the Proposition.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lemma:generic-regret-bound}]
By Fenchel-Young inequality,
\begin{align*}
\sum_{t=1}^T \left( R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) \right)
& = R_{T+1}^*(-L_T) - R_1^*(0) \\
& \ge - \langle L_T, u \rangle - R_{T+1}(u)  - R_1^*(0) \\
& = - R_{T+1}(u)  - R_1^*(0) - \sum_{t=1}^T \langle \ell_t, u \rangle \; .
\end{align*}
We add $\sum_{t=1}^T \langle \ell_t, w_t \rangle$ to both sides and we obtain
$\Regret_T(u)$ on the right side. After rearrangement of the terms, we get an upper bound
on the regret:
\begin{align*}
\Regret_T(u)
& = \sum_{t=1}^T \langle \ell_t, w_t \rangle - \sum_{t=1}^T \langle \ell_t, u \rangle \\
& \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^T \left( R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, w_t \rangle \right) \; .
\end{align*}
By Proposition~\ref{proposition:conjugate-properties}, property 2, we have $w_t =
\grad R_t^*(-L_{t-1})$ and therefore we can rewrite the sum in last expression as
\begin{align*}
& \sum_{t=1}^T R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, w_t \rangle \\
& = \sum_{t=1}^T R_{t+1}^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, \grad R_t^*(-L_{t-1}) \rangle \\
& = \sum_{t=1}^T R_t^*(-L_t) - R_t^*(-L_{t-1}) + \langle \ell_t, \grad R_t^*(-L_{t-1}) \rangle - R_t^*(-L_t) + R_{t+1}^*(-L_t) \\
& = \sum_{t=1}^T \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
\end{align*}
This finishes the proof.
\end{proof}

### 2015-12-08 preliminaries.tex
Replace subscript "s" with "i"
Many improvements
1) Add conclusion
2) Add limits and their explanations
3) Add many bibliographic references
4) Fix formatting for most .tex files

Let $V$ be a finite-dimensional real vector space equipped with a norm
$\|\cdot\|$. We denote by $V^*$ its dual vector space.  The bi-linear map
associated with $(V^*, V)$ is denoted by $\langle \cdot, \cdot \rangle:V^*
\times V \to \R$.  The dual norm of $\|\cdot\|$ is $\|\cdot\|_*$.

@@

\begin{algorithm}[t]
\caption{\textsc{FTRL with Varying Regularizer}}
\label{algorithm:ftrl-varying-regularizer}
\begin{algorithmic}[1]
\STATE Initialize $L_0 \leftarrow 0$
\FOR{$t=1,2,3,\dots$}
\STATE Choose a regularizer $R_t:K \to \R$
\STATE $w_t \leftarrow \argmin_{w \in K} \left( \langle L_{t-1}, w \rangle + R_t(w) \right)$
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE $L_t \leftarrow L_{t-1} + \ell_t$
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader} (\textsc{FTRL}) algorithm with varying regularizers,
presented as Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The following
lemma bounds its regret.

>>>>

Let $V$ be a finite-dimensional\footnote{Many, but not all, of our
results can be extended to more general normed vector spaces.} real vector
space equipped with a norm $\|\cdot\|$. We denote by $V^*$ its dual vector
space.  The bi-linear map associated with $(V^*, V)$ is denoted by $\langle
\cdot, \cdot \rangle:V^* \times V \to \R$.  The dual norm of $\|\cdot\|$ is
$\|\cdot\|_*$.

@@

\begin{algorithm}[t]
\caption{\textsc{FTRL with Varying Regularizer}}
\label{algorithm:ftrl-varying-regularizer}
\begin{algorithmic}[1]
\REQUIRE Non-empty closed convex set $K \subseteq V$
\STATE Initialize $L_0 \leftarrow 0$
\FOR{$t=1,2,3,\dots$}
\STATE Choose a regularizer $R_t:K \to \R$
\STATE $w_t \leftarrow \argmin_{w \in K} \left( \langle L_{t-1}, w \rangle + R_t(w) \right)$
\STATE Predict $w_t$
\STATE Observe $\ell_t \in V^*$
\STATE $L_t \leftarrow L_{t-1} + \ell_t$
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

Our scale-free online learning algorithms are versions of the \textsc{Follow
The Regularized Leader}\footnote{The name \textsc{Follow The Regularized
Leader} comes from~\cite{Abernethy-Hazan-Rakhlin-2008}. Independently, the
algorithm was proposed by~\cite{Nestorov-2009} under the name \textsc{Dual
Averaging} and was later anlyzed in~\cite{Xiao-2010}.} (\textsc{FTRL})
algorithm with varying regularizers, presented as
Algorithm~\ref{algorithm:ftrl-varying-regularizer}. The algorithm is
paramatrized by a sequence $\{R_t\}_{t=1}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}.  Each regularizer $R_t$ can depend on the
past loss vectors $\ell_1, \ell_2, \dots, \ell_{t-1}$ in an arbitrary way.  The
following lemma bounds its regret.
